What is long-distance dispersal? And a taxonomy of dispersal events\\ \vspace{2cm}

### 2016-10-10 Data/kernels.Rmd
Added distances.txt

# Prunus mahaleb dispersal distances data. -------------------------------
# Get the data from my GitHub repository.
link = "https://raw.githubusercontent.com/pedroj/dispkernels/master/distances.txt"
file = "distances.txt"
if(!file.exists(file)) download(link, file, mode = "wb")
assdist <- read.table(file, sep = "\t", dec = ",", 
    header = TRUE, na.strings="NA")
str(assdist)

>>>>

# Prunus mahaleb dispersal distances data. -------------------------------
# Get the data from my GitHub repository.
link = "https://raw.githubusercontent.com/pedroj/dispkernels/master/Datasets/distances.txt"
file = "distances.txt"
if(!file.exists(file)) download(link, file, mode = "wb")
assdist <- read.table(file, sep = "\t", dec = ",", 
    header = TRUE, na.strings="NA")
str(assdist)

### 2016-10-10 Manuscript/MS- What is LDD.tex
Added distances.txt

A second consideration in terms of spatial boundaries, with effects on dispersal patterns, is the genetic neighborhood area $N^b_e$, i.e., the spatial extent including a subset of panmictic individuals within a population \citep{Wright:1943aa,Wright:1946aa}. Thus, the $N^b_e$ area can be equal to the whole extent of the population whenever the population is unstructured and there is evidence for random mating events among all the individuals. However, most populations and stands of long-lived trees show highly aggregated and clumped distributions \citep{Seidler:2006hx}, where relatively long distances may separate groups of individuals within the same population. In these cases we might expect $N^b_e$ area to be substantially smaller than the total population area. Therefore, at least four possible scenarios exist with distinct implications in terms of consequences for dispersal (Table 1). In the case of dispersal events not extending beyond the geographic limits of the population or reference area, actual LDD events may involve dissemination beyond a reduced neighborhood area that is smaller than the geographic extent of the population, originating local long-distance ($LDD_{loc}$) dispersal events (Table 1, Fig. 2A). Actual short-distance dispersal would then involve those situations where the propagule is disseminated within \textit{both} the population limits and the genetic neighborhood boundary ($SDD_{loc}$). Along a similar reasoning, dispersal events outside the population limits will not necessarily convey LDD (Table 1, Fig. 2B): this is expected in cases where the genetic neighborhoods are extensive, going beyond the geographic limits of local populations, as in fig trees \citep{Nason:1998aa} with long-distance pollination, generating LDD events within the genetic neighborhood ($LDD_{neigh}$). Note that pollen and seeds may have contrasting movement patterns in rference to the distinct spatial scales of the population limits and of the genetic neighbourhood. For example, wind-dispersed species with reduced seed mobility (in terms of distance), such as oaks, can have large genetic neighbourhoods with extensive pollen dispersal \citep{Streiff99} \citep[but see, e.g.,][for fragmented stands]{Smouse:2001aa,Dutech:2005fk} so that $LDD_{neigh}$ dispersal events might frequently move beyond the physical limits of the population, patch, or stand but remain within the genetic neighbourhood. Finally, strict-sense LDD events would involve dissemination outside \textit{both} the population limits and the genetic neighborhood boundary ($LDD_{ss}$) (Table 1, Fig. 2A).

While both $SDD_{loc}$ and $LDD_{loc}$ can be crucial for assuring the local persistence of populations, $LDD_{neigh}$ and $LDD_{ss}$ would be extremely important contributors to the structuring of genetic pools, realized gene flow, and maintaining connectivity in metapopulation scenarios. I argue that both the demographic and the genetic references are relevant for a proper definition of LDD.

>>>>

A second consideration in terms of spatial boundaries, with effects on dispersal patterns, is the genetic neighborhood area $N^b_e$, i.e., the spatial extent including a subset of panmictic individuals within a population \citep{Wright:1943aa,Wright:1946aa}. Thus, the $N^b_e$ area can be equal to the whole extent of the population whenever the population is unstructured and there is evidence for random mating events among all the individuals. However, most populations and stands of long-lived trees show highly aggregated and clumped distributions \citep{Seidler:2006hx}, where relatively long distances may separate groups of individuals within the same population. In these cases we might expect $N^b_e$ area to be substantially smaller than the total population area. Therefore, at least four possible scenarios exist with distinct implications in terms of consequences for dispersal (Table 1). In the case of dispersal events not extending beyond the geographic limits of the population or reference area, actual LDD events may involve dissemination beyond a reduced neighborhood area that is smaller than the geographic extent of the population, originating local long-distance ($LDD_{loc}$) dispersal events (Table 1, Fig. 2A). Actual short-distance dispersal would then involve those situations where the propagule is disseminated within \textit{both} the population limits and the genetic neighborhood boundary ($SDD_{loc}$). Along a similar reasoning, dispersal events outside the population limits will not necessarily convey LDD (Table 1, Fig. 2B): this is expected in cases where the genetic neighborhoods are extensive, going beyond the geographic limits of local populations, as in fig trees \citep{Nason:1998aa} with long-distance pollination, generating LDD events within the genetic neighborhood ($LDD_{neigh}$). Note that pollen and seeds may have contrasting movement patterns in reference to the distinct spatial scales of the population limits and of the genetic neighbourhood. For example, wind-dispersed species with reduced seed mobility (in terms of distance), such as oaks, can have large genetic neighbourhoods with extensive pollen dispersal \citep{Streiff99} \citep[but see, e.g.,][for fragmented stands]{Smouse:2001aa,Dutech:2005fk} so that $LDD_{neigh}$ dispersal events might frequently move beyond the physical limits of the population, patch, or stand but remain within the genetic neighbourhood. Finally, strict-sense LDD events would involve dissemination outside \textit{both} the population limits and the genetic neighborhood boundary ($LDD_{ss}$) (Table 1, Fig. 2A).

While both $SDD_{loc}$ and $LDD_{loc}$ can be crucial for assuring the local persistence of populations, $LDD_{neigh}$ and $LDD_{ss}$ would be extremely important contributors to the structuring of genetic pools, realized gene flow, and maintaining connectivity in metapopulation scenarios. I argue that both the demographic and the genetic references are relevant for a proper definition of LDD. These differences may have different implications in relation to the dispersal biology of species. For example, frugivorous vertebrates, particularly the large-sized ones, tend to disperse a high number of half-sibs propagules, from the same mother tree to the same deposition site \citep{Jordano:2000ft}, potentially increasing the frequency of $LDD_{neigh}$ events if dispersal distances are relatively short.
